### 2017-09-30 Graduate - Introduction to Analysis I/Assignment 4/4-homework20170925.tex
add problem 3
Add problem 4

@@

\item  (Problem 15, Page 365)  A sequence $\{f_n\}$ of measurable real-valued functions on $X$ is said to \emph{converge in measure} to a measurable function $f$  provided that for each $\eta > 0$, \[
\lim_{n\to \infty} \mu\{x\in X \mid |f_n(x) - f(x)|>\eta \} = 0.\]A sequence $\{f_n\}$ of measurable functions is said to be \emph{Cauchy in measure} provided that for each $\epsilon > 0$ and $\eta > 0$, there is an index $N$ such that for each $m,n\geq N$, \[
\mu\{x\in X \mid |f_n(x) - f_m(x)| > \eta \} < \epsilon.\]
\begin{enumerate}
\item Show that if $\mu(X)< \infty$ and if $\{f_n\}$ converges pointwise a.e. on $X$ to a measurable function $f$, then $\{f_n\}$ converges to $f$ in measure.
\item Show that if $\{f_n\}$ converges to $f$ in measure, then there is a subsequence of $\{f_n\}$ that converges pointwise a.e. to $f$.
\item Show that if $\{f_n\}$ is Cauchy in measure, then there is a measurable function $f$ to which $\{f_n\}$ converges in measure.\end{enumerate}

>>>>

\textbf{Solution:}
Notice that for each $r\in \mathbb{R}\supset\mathbb{Q}$, we have
$$
\{x\in X\mid f(x) < r\} = \bigcup_{\substack{c < r \\ c \in \mathbb{Q}}}\{x\in X\mid f(x) < c\}.
$$
Then since Lebesgue measurable sets make a $\sigma-$Algebra, we know $\{x\in X\mid f(x) < r\}$ is measurable. On the other hand, since each rational number is a real number, the other direction stands.
\bigskip

@@

\textbf{Solution:}
Denote
$$
E_n = \{x\in X\mid |f_n(x)-f_{n+1}(x)|>\frac{1}{2^n}\},
$$
Then 
$$
\bigcup_{n=1}^{\infty}\mu(E_n) < \sum_{n=1}^{\infty}\mu(E_n) < \sum_{n=1}^{\infty}\frac{1}{2^n} = 1.
$$
According to Borel-Cantelli Lemma, $\exists E_0$, $\mu(E_0) = 0$, s.t. $\forall x\in X\setminus E_0$, $x$ belongs to at most finite number of $E_n$. That means, $\forall x\in X\setminus E_0$, $\exists N > 0$, $\forall n > N$, $x\in E_n$. So 
$$
|f_n(x)-f_{n+1}(x)| < \frac{1}{2^n}.
$$
Thus 
$$
\forall m > n, |f_m(x)-f_{n}(x)| < \sum_{i=n}^{m-1}|f_{i+1}(x)-f_i(x)| < \frac{1}{2^{n-1}}.
$$
This means that $f_n(x)$ is a Cauchy sequence, then it converges. Thus $\{f_n\}$ is pointwise convergent on $X\setminus E_0$, and thus is pointwise convergent a.e. on $X$.
\bigskip

\item  (Problem 15, Page 365)  A sequence $\{f_n\}$ of measurable real-valued functions on $X$ is said to \emph{converge in measure} to a measurable function $f$  provided that for each $\eta > 0$, \[
\lim_{n\to \infty} \mu\{x\in X \mid |f_n(x) - f(x)|>\eta \} = 0.\]A sequence $\{f_n\}$ of measurable functions is said to be \emph{Cauchy in measure} provided that for each $\epsilon > 0$ and $\eta > 0$, there is an index $N$ such that for each $m,n\geq N$, \[
\mu\{x\in X \mid |f_n(x) - f_m(x)| > \eta \} < \epsilon.\]
\begin{enumerate}
\item Show that if $\mu(X)< \infty$ and if $\{f_n\}$ converges pointwise a.e. on $X$ to a measurable function $f$, then $\{f_n\}$ converges to $f$ in measure.
\item Show that if $\{f_n\}$ converges to $f$ in measure, then there is a subsequence of $\{f_n\}$ that converges pointwise a.e. to $f$.
\item Show that if $\{f_n\}$ is Cauchy in measure, then there is a measurable function $f$ to which $\{f_n\}$ converges in measure.
\end{enumerate}

\textbf{Solution:}
